### 2014-03-16 HowtoHowtoCapon/submission/submit1/answer/answer.tex
la2pdf commit - 2014:03:16	23:46:31	(Sun16.Mar)

\ai{We agree with the reviewer that this should be improved. We still state the two order of magnitude improvement over our reference implementation as this ``total payoff'' of our efforts, but also state that this figure would likely be 5-10 had the CPU side received similar treatment.}

@@

\ai{We thank the reviewer for these corrections (8.-10.). Corrections applied.}

>>>>

\ai{We agree with the reviewer that this should be improved. We still state the two order of magnitude improvement over our reference implementation as a "total payoff" for our efforts, but now also state that this figure would likely be 5-10 had the CPU side received similar treatment.}

@@

\ai{We thank the reviewer for these corrections (8.-10.). They are all applied.}
